MachLLensFinder - I: A Machine Learning Strong Lensing Identification Pipeline

### 2016-11-05 ms.tex
added grid search results

@@

%-------------------------------------------------%
\section{Results}
\label{sec:results}
%-------------------------------------------------%

>>>>

**Results of Grid search across the parameters of the pipeline**

@@

%-------------------------------------------------%
\section{Results}
\label{sec:results}
%-------------------------------------------------%
%-------------------------------------------------%
\subsection{Optimized pipeline parameters}
%-------------------------------------------------%

\begin{table}
\caption{Grid Search of Pipeline Parameters}
\begin{center}
\begin{tabular}{cccccc}
\hline \\ [-0.2cm]
N$_{orient}$ & Pixels/Cell & Cells/Block & LogReg$_{\text{coeff}}$ & HOG size & Score \\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(a) HST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
9 & (4, 4) & (3, 3) & 50. & &$0.76181\pm0.00491$\\ [0.2cm]
9 & (4, 4) & (1, 1) & 50. & &$0.83403\pm0.00547$\\ [0.2cm]
9 & (8, 8) & (3, 3) & 50. & &$0.85417\pm0.00851$\\ [0.2cm] 
9 & (8, 8) & (1, 1) & 50. & &$0.86389\pm0.00687$\\ [0.2cm] 
9 & (16, 16) & (1, 1) & 50. & & $0.88542\pm0.00680$ \\ [0.2cm]
9 & (16, 16) & (3, 3) & 10. & &$0.89306\pm0.00687$ \\ [0.2cm]
8 & (16, 16) & (3, 3) & 50. & &$0.90000\pm0.00170$ \\ [0.2cm]
9 & (16, 16) & (3, 3) & 50. & &$0.90139\pm0.00804$ \\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(b) LSST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
& & & & &\\
& & & & &\\ [0.2cm]
\hline
\end{tabular}
\end{center}
\label{tab:gridsearch}
\tablecomments{Panel (a) shows the results of a grid search across a
  range of HOG parameters and regression coefficient with training and
  test sets of size 1440 with the HST-like mock dataset.  Panel (b)
  shows the corresponding results for training and test sets of size
  5760 with the LSST mock dataset.  We explore different HOG
  parameters in each dataset due to resolution and image size
  differences.}
\end{table}

We run a grid search across parameters that should reasonably sample
the arc edges in either the HST- or LSST-like mock observations.
Recall, the HST-like images are $300\times300$ pixels per image, while
the LSST-like mock observations are $45\times45$ pixels per image.  In
general, must run a grid search in order to best optimize the pipeline
parameters.

We must first estimate the size of a cell that will contain a coherent
arc feature.  To first order approximation, subdivisions of cells that
are 1/100th the area of the entire image should contain coherent arc
edges that span an elongated shape within arc-containing cells.
Therefore, we perturb the pixels per cell parameter about (30, 30) for
the HST-like images, and (4, 4) for the LSST-like images.

Next, the cells per block parameter determines the normalization of
each cell with respect to the neighboring cell.  In general, this will
downweight arc-like edges in cells that neighbor very bright cells,
such as cells that cover the BCG.  We therefore vary the cells per
block parameter between (1, 1) and (3, 3).

The number of orientations will determine the sampling of rounded
edges.  For example, if we only have two orientations, an arc-like
feature in a cell will appear as .... However, contributions from a
cluster or line-of-sight galaxy in the same cell will ... the
normalizations in the histogram.  The resolution of the overall image
will also limit the additional information that an increase in
$N_\text{orientations}$ will provide.  For the LSST-like data,
$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$ only
results in a $???\%$ improvement.  In the case of the HST-like data,
$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$
results in a $???\%$ improvement.

Note, we also include the size of the extracted features, e.g. the
length of the HOG.  Larger features will increase the amount of time
required to train a model, and also impact memory restrictions on the
size of the training set.  The logistic regression coefficient will
also increase the training time.  We discuss the score dependence on
logistic regression coefficient in Section\ref{sec:unregularizedfit}.

\subsection{Scores vs. regularization on larger train/test set with comparable grid search in parameterization}\label{sec:unregularizedfit}

\subsection{False positives/negatives and why... something about likely images given cosmology}

\subsection{ROC curve}

\subsection{Effects of BCG contamination}
